---
title: "JoeNumainvilleTools Examples"
author: "Joe Numainville"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Examples
```{r}
library(JoeNumainvilleTools)
library(ggplot2)
library(dplyr)
```

%xax% computes the transverse of a vector x multiplied by the inverse of matrix a multiplied by x
```{r}
a <- matrix(c(3,8,7,1), nc = 2, nr = 2)
x <- c(1,2)
a %xax% x
```

xax works similarly, but in normal function notation
```{r}
a <- matrix(c(3,8,7,1), nc = 2, nr = 2)
x <- c(1,2)
xax(a,x)
```

ggplot_Wrapper is a wrapper hat plots a ggplot scatter plot, with an optional color
```{r}
ggplot_wrapper(food_coded, food_coded$GPA, food_coded$weight, as.factor(food_coded$Gender))
ggplot_wrapper(food_coded, food_coded$GPA, food_coded$weight)
```

mle calculates the maximum likelihood estimate of a vector for the gamma distribution
```{r}
x <- c(1,2,3)
mle(x)
```

opt is similar, but can take varying distributions and intervals
```{r}
x <- c(1,2)
logl <- function(alpha, x) {sum(dgamma(x, shape = alpha, log = TRUE))}
interval <- mean(x) + c(-1, 1) * 3 * sd(x)
opt(x, logl, interval)
```

myapply is like apply, but only works on margin 1 and 2
```{r}
a <- matrix(1:9, nrow = 3, ncol = 3)
myapply(a, 1, mean)
myapply(a, 2, mean)
```

slice filters a column in some data so it meets the specified value
```{r}
x <- c (1,2,2,3)
y <- c (2,2,2,2)
df <- data.frame(x,y)
slice(df, df$x, 2)
slice(df, df$y, 2)
```

standardize calculates (x - mean(x))/sd(x) for each column in a given matrix
```{r}
a <- array(1:9, dim=c(3,3))
standardize(a)
```

summFunc gives a mean, variance, and standard deviation of a number vector in a list
```{r}
x <- c(-3, 0, 3,1)
mean <- sum(x) / length(x)
var = sum((x - mean)^2)/length(x)
sd = sqrt(var)
summFunc(x)  
```

weigtedSumm acts in a similar fashion, but also takes a vector p that adds up to 1 that gives each element in x a weight
```{r}
x <- c(1,2,3)
p <- c(.1,.2,.7)
mean = sum(p * x)
var = sum(((x - mean) ^ 2) * p)
sd = sqrt(var)
weightedSumm(x,p)
```
